NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PE, PG and PS lipids

### 2017-10-23 Manuscript/manuscript.tex
Update PS figure

\subsection{PS headgroup}
Order parameters for bilayers with PS headgroups
from different experiments and simulations are shown in
Figs. \ref{HGorderParametersDOPS} and  \ref{HGorderParametersPOPS}.
None of the tested models gives satisfactory agreement with
experiments for order parameters in headgroup $\alpha$ and $\beta$
carbons.
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersDOPS.eps}
  \caption{\label{HGorderParametersDOPS}
    Order parameters for DOPS headgroup and glycerol
    backbone from simulations with different models and experiments without CaCl$_2$ 
    Experimental data from \cite{browning80} contains 0.1M of NaCl.
    Signs are taken from experiments for POPS described in Supplementary Information.
  }
\end{figure}
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPOPS.eps}
  \caption{\label{HGorderParametersPOPS}
    Headgroup and glycerol backbone order parameters for systems with POPS 
    from simulations with different models and experiments \cite{roux90}.
    Signs are taken from experiments described in Supplementary Information.
  }
  \todo{More simulation data for lipids with different headgroups to be collected} \\
  \todo{Some simulations contain potassium as counterions, while some sodium.
    All experiments here contain some amount of sodium salt. The best
    ion concentrations for comparison should be figured out.} \\
  \todo{Why there is difference between CHARMM36 simulation results from POPS:POPC mixture and
  pure POPS? Discussion in https://github.com/NMRLipids/NMRlipidsIVotherHGs/issues/1}
\end{figure}

@@

>>>>

\subsection{PS headgroup}
The headgroup order parameters of DOPS and POPS bilayers 
from different experiments and simulations are shown in
Figs. \ref{HGorderParametersPS}.
None of the tested models gives satisfactory agreement with
experiments for order parameters in headgroup $\alpha$ and $\beta$
carbons.
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPS.eps}
  \caption{\label{HGorderParametersPS}
    Order parameters for DOPS headgroup and glycerol
    backbone from simulations with different models and experiments without CaCl$_2$ 
    Experimental data from \cite{browning80} contains 0.1M of NaCl.
    Signs are taken from experiments for POPS described in Supplementary Information.
  }
  \todo{Check and report all the counterions.}
  \todo{Glycerol backbone order parameters should be available from the spectra measured by Tiago Ferreira.}
\end{figure}

@@

\section{Lipid bilayers with mixed compositions}

\subsection{PC/PS mixtures}
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPOPS.eps}
  \caption{\label{HGorderParametersPOPS}
    Headgroup and glycerol backbone order parameters for systems with POPS 
    from simulations with different models and experiments \cite{roux90}.
    Signs are taken from experiments described in Supplementary Information.
  }
  \todo{Some simulations contain potassium as counterions, while some sodium.
    All experiments here contain some amount of sodium salt. The best
    ion concentrations for comparison should be figured out.} \\
  \todo{Why there is difference between CHARMM36 simulation results from POPS:POPC mixture and
  pure POPS? Discussion in https://github.com/NMRLipids/NMRlipidsIVotherHGs/issues/1}
\end{figure}
